\documentclass[13pt,twoside,a4paper]{article}
\usepackage{url}
\usepackage{hyperref}

\begin{document}
\title{Portfolio pracy własnej}
\author{Patryk Lisik}
\date{January 2024}
\maketitle

\section*{Article -- How to be a -10x Engineer} 
Chosen \href{https://taylor.town/-10x}{article -- How to be a -10x Engineer}: \href{https://taylor.town/-10x}{\url{https://taylor.town/-10x}}

\subsection*{Summary}

Article is a humorous satire of the corporate workplace, which wastes tons of engineering hours.
Author defines $-10x$ engineer as a person who can void 400 hours of 10 other people work per week, while
delivering nothing in that time.
400 hours comes from 40h per person per week.
First way of wasting so much time is through miscommunication like fruitless technical discussions that lead to nowhere,
    calls with unnecessary people that are have no input to the discussed topic or just making other people unhappy.
Time is money, so can be wasted via payment to third parties for build/deployment time or missed business opportunities.
A third way to waste time is to hire people that do nothing or even better if they are actively sabotaging the work of others.
Article sarcastically emphasises importance of keeping them at work.
This way you do not have to waste all those hours yourself. 
The last method of $-10xing$ is to create undebugable software that causes giant overhead on ticket management level. 

\subsection*{Words}

\begin{description}
    \item[Foist blame] Act of shifting the blame onto someone, to avoid accountability   
    \item[Sow confusion] Act of creating state of chaos and ambiguity.
    \item[Futile] Something incapable of producing meaningful outcome.
    \item[Skunkwork project] Internal innovative or unconventional project that is conducted
                                outside typical business proces of organization.  
    \item[Incur ] Verb that means to become subject of consequences. 
    \item[Triage] Process of categorizing thing based of their level of urgency of importance.
    \item[Context-switching] Process of shifting attention and focus from one thing to another. 
    \item[Inconspicuously] Adverb that describes action that draws no attention or is deliberately subtle.

\end{description}

\end{document}
